\documentclass[12pt]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=cyan,
}

\pagenumbering{gobble}

\begin{document}

\noindent Hey folks!

\vspace{\baselineskip}
My name's David!  I'm writing to you in response to your posting for an
``Ethereum Core Developer'' on the OpenEthereum client project.  I'm psyched to
be reaching out to you about this role!  Let me tell you a bit about my
background and why I think I'd be a great fit at Gnosis.

The four most recent years of my career have been dedicated to distributed
computing work.  I spent over two of those years at the Ethereum Foundation on
the Snake Charmers team.  With the Snake Charmers, I helped to maintain the
core collection of open source Python libraries that are used for Ethereum
blockchain development with Python.  This included libraries such as
\href{https://github.com/ethereum/eth-abi}{eth-abi} and
\href{https://github.com/ethereum/web3.py}{web3.py}.  Some of those libraries
were used by the Python-based Trinity client.  I was also involved in efforts
to standardize package registry contracts as well as the contract JSON ABI
format and ABI encoding format.

Towards the end of my time with the Snake Charmers, I founded the
\href{https://github.com/ethereum/fe}{Fe project} (initially called Rust
Vyper).  Fe is written in Rust and was originally intended to be a next
generation version of the Vyper compiler.  At this point, it has deviated
significantly from the Vyper project and is a separate project with different
goals.  It's currently being maintained by a pair of talented devs at the
Foundation one of whom is my former colleague Christoph Burgdorf from the Snake
Charmers team.

I've spent the last year and some months in the high performance computing
space and am interested in moving back into blockchain work.  During my time at
the Foundation, I had always intended to become more involved in client and
protocol work if I found the opportunity.  The OpenEthereum project seems like
an ideal way to achieve that goal.  I have significant domain knowledge
concerning the Ethereum network from my time with the EF\@.  I've founded a
significant project using the Rust language in the Ethereum space.  I also have
experience with other systems languages such as C++ from other positions I've
held during my career.  For all these reasons, I think I'd be a great fit for
the OpenEthereum project!

I sincerely hope to hear back from you!

\vspace{\baselineskip}
\noindent Cheers,

\noindent David Sanders
\end{document}
